\documentclass{beamer}
\usepackage{minted}
\usepackage{inconsolata}
%\usepackage{enumitem}
%\setitemize{topsep=0pt,parsep=0pt,partopsep=0pt}

\renewcommand{\insertnavigation}[1]{}
\setbeamertemplate{frametitle}[default][left]
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{headline}{}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{natbib}

\usepackage{xpatch}
\xpatchcmd{\itemize}
  {\def\makelabel}
  {%
    \addtolength{\itemsep}{-1ex}%
    \def\makelabel%
  }
  {}
  {}

\BeforeBeginEnvironment{itemize}{\vskip-1ex}

\definecolor{LogicBlue}{RGB}{204,0,0}
\definecolor{InferenceRed}{RGB}{212,55,59}
\usetheme{Warsaw}
\setbeamercolor{structure}{fg=InferenceRed}
\setbeamercolor{frametitle}{bg=LogicBlue, fg=white}
\setbeamertemplate{navigation symbols}{}   

\AtBeginSection[]{
  \begin{frame}
  \vfill \centering
  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

\usemintedstyle{tango}
\setminted{fontsize=\fontsize{6}{7}\selectfont,frame=lines,framerule=1pt,rulecolor=\color{gray!40}}

\title{How to  Write an AI (in under 500 lines)}
\subtitle{Multi-objective Sequential Model Optimization}
\author{{\bf Tim Menzies}\\ \href{mailto:youremail@example.com}{timm@ieee.org} \\ \href{http://yourhomepage.com}{http://timm.fyi}}
\institute{Computer Science }
\date{\today}

\begin{document}
\maketitle
\small

\begin{frame}[fragile]\frametitle{Problem}
Too many choices, not enough time to look at them all.
\begin{itemize}
\item e.g. Hundreds of cars in a car yard, you try three, then buy one;
\item e.g. You can't test everything -- so you just test a few;
\item e.g. Software has $10^9$ of options -- but you  have time to try a few.
\end{itemize}
So lets apply {\em sequential model optimization}:
\begin{itemize}
\item \citet{xia2020sequential}, 
\citet{hutter2011sequential},
\citet{nair2018finding},
\citet{hsu2018arrow},
\citet{mockus1989bayesian},
\citet{golovin17}



\item e.g. Hundreds of cars in a car yard, you try three, then buy one;
Some terminology
\[ \underbrace{y_1,y_2,...}_{\mathit{}dependent\;variables,\;goals} = f(\underbrace{x_1, x_2, x_3, x_4, x_5, x_6,....}_{\mathit{indendepent variables}})
\]
\end{itemize}
\begin{itemize}
\item 
\item But depndent variables are more expesnive to collect 
\item e.g. A supermarket has 100 apples. Which ones are tasty?
So lets walk data incrementally:
\end{itemize}
\end{frame}


\begin{frame}[fragile]\frametitle{Problem}
Too many choices, not enough time to look at them all.
\begin{itemize}
\item adas
\end{itemize}
\begin{columns} \begin{column}{.3\textwidth}
asdaasasa
\end{column}\begin{column}{.7\textwidth}\begin{minted}{lua}
function NUM.new(i,at,txt) --> NUM;  constructor; 
  i.at, i.txt = at or 0, txt or "" -- column position 
  i.n, i.mu, i.m2 = 0, 0, 0
  i.lo, i.hi = math.huge, -math.huge 
  i.w = i.txt:find"-$" and -1 or 1 end
\end{minted}
\end{column}\end{columns}
\end{frame}

\section{Test section one}

\begin{frame}
\frametitle{What is Prolog?}
\begin{itemize}
    \item A programming language associated with artificial intelligence and computational linguistics.
    \item Based on formal logic.
    \item Declarative: Describe the problem, not how to solve it.
    \item Known for its ability to handle symbolic reasoning and knowledge representation.
\end{itemize}
\end{frame}


\begin{frame}
\begin{columns}
\begin{column}{0.5\textwidth}
   some text here some text here some text here some text here some text here
\end{column}
\begin{column}{0.5\textwidth}  %%<--- here
    \begin{center}
       asdsa
     \end{center}
\end{column}
\end{columns}
\end{frame}

\section{References}
 \begin{frame}[allowframebreaks]
         \frametitle{References}
         \bibliographystyle{natbib}
         {\tiny \bibliography{slides.bib}}
 \end{frame}


\end{document}
